
\section*{Version 0}

\paragraph{0.0.0 - 18.11.2019}

\begin{itemize}
\item Created the git repository
\item Copied the template for the KIT bachelors degree to be used as the basis of this document
\item Added a first version of the "premise" chapter and "document overview"
\item Added chapter about the system requirements of the unreal engine.
\end{itemize}

\paragraph{0.0.1 - 19.11.2019}

\begin{itemize}
\item Added the chapter about installing unreal engine
\item Added the chapter about the other application
\end{itemize}

Possible improvements in the future:

\begin{itemize}
\item Extend the other application chapter with the list of all the applications that was given in the book
\end{itemize}

\paragraph{0.0.2 - 21.11.2019} 

\begin{itemize}
\item Added a draft of the chapter about design choices. The chapter
\begin{itemize}
\item Section about the scope of the project: Rather make the scope smaller, because a VR game is a lot of work
\item Section about "Why VR?" why should you even make a VR project. Could traditional media do the same?
\item Section about the method of locomotion in VR. Why teleportation might be a good idea.
\end{itemize}
\item Began working on the "ressources" chapter, which is supposed to list a few helpful ressources (books mainly) in the pursuit of making a VR representation
\end{itemize}

\paragraph{0.0.3 - 22.11.2019}

\begin{itemize}
\item Wrote the chapter about the book "Unreal for mobile and standalone VR"
\item removed the appendix section for now. Since I dont need that yet.
\item removed the inclusion of the preamble.tex
\item removed the inclusion of the list of tables for now
\item Added preliminary sections for the "tutorials" section.
\end{itemize}

% What has to be done for the first version of this document
% - Wirte the tutorials, that I wanted to write
% - Fix the missing citations and stuff in the other chapters

\paragraph{0.0.4 - 26.11.2019}

\begin{itemize}
\item Added all the missing citations
\item Decided, that for the first version there will only be a sequencer section in the tutorials chapter
\item Started to write the sequencer tutorial
\end{itemize}

% for the next version
% - Finish writing the sequencer tutorial
% - Add images to the sequencer tutorial

